\newpage
\chapter*{List of Publications}\markboth{List of Publications}{}
%\section{Related Publication}

\noindent \textbf{Refereed Journal Papers}
\begin{itemize}
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Critical Sensor Density for Partial Coverage under Border Effects in Wireless Sensor Networks'', IEEE Transactions on Wireless Communications, vol. 13, no. 5, pp. 2374-2382, March 2014. [Chapter~\ref{cse}]
\end{itemize}

\noindent \textbf{Refereed Conference Papers}
\begin{itemize}
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Analysis of Stochastic k-Coverage in Wireless Sensor Networks with Boundary Deployment'', In Proc. of IEEE WCNC, Istanbul, Turkey, April 2014. [Chapter~\ref{ITS}]
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Critical Sensor Density for Fault-tolerant Coverage in 3D Heterogeneous Wireless Sensor Networks'', In Proc. of IEEE ANTS, Chennai, India, December 2013. [Chapter~\ref{3dcc}]
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Analysis of the Redundancy in Coverage of A Heterogeneous Wireless Sensor Network'', In Proc. of IEEE ICC, pages 1904 - 1909, Budapest, Hungary, June 2013. [Chapter~\ref{3d}]
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Sleep Scheduling for Partial Coverage in Heterogeneous Wireless Sensor Networks'', In Proc. of COMSNETS,  pages 1-10, Bangalore, India, January 2013. [Chapter~\ref{2d}]
\end{itemize}

\noindent \textbf{Poster Presentations}
\begin{itemize}
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Minimum Sensor Density for Coverage in Sensor Networks'', In ACM MobiHoc, Bangalore, July 2013 (Recent Results poster). [Chapter~\ref{cse}]
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Critical Sensor Density for Connectivity in Heterogeneous Wireless Sensor networks'', In ACM MobiHoc, Bangalore, July 2013 (Recent Results poster). [Chapter~\ref{ITS}]
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Analysis on the Redundancy of A Heterogeneous Wireless sensor Network'', In $8^{th}$ TCS Technical Architects Global Conference, Delhi, India, May 2012 (Poster). [Chapter~\ref{cse}]
\end{itemize}

\noindent \textbf{Journals Papers Under Review}
\begin{itemize}
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Analysis of Stochastic $k$-Coverage and Connectivity in Sensor Networks with Boundary Deployment'', IEEE Transactions on Intelligent Transportation Systems. [Chapter~\ref{ITS}]
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Analysis of Stochastic Coverage and Connectivity in 3D Heterogeneous Directional Sensor Networks'', Elsevier Pervasive and Mobile Computing. [Chapter~\ref{3dcc}]
\item   \textbf{Hari Prabhat Gupta}, S.V. Rao, and T. Venkatesh, ``Sleep Scheduling Protocol for $k$-Coverage of Three-Dimensional Heterogeneous Wireless Sensor Networks'', IEEE Transactions on Wireless Communications. [Chapter~\ref{3d}]
\end{itemize}
